\documentclass[conference]{IEEEtran}
\usepackage{graphicx}
\usepackage{booktabs}
\title{Assignment 2: Baseline Pipeline for QEvasion}
\author{Student A \and Student B \and Student C \\ CS-272: Artificial Intelligence}
\begin{document}
\maketitle
\begin{abstract}
We implement three baseline models for the QEvasion task: (A) TF-IDF + Logistic Regression, (B) Bi-LSTM, and (C) TF-IDF + Linear SVM. This report summarizes the pipeline, hyperparameters and validation results.
\end{abstract}
\section{Pipeline Overview}
The pipeline consists of: data loading $\rightarrow$ preprocessing (tokenization, TF-IDF / sequences) $\rightarrow$ baseline models $\rightarrow$ evaluation. All figures and plots are saved as PDF in the \texttt{plots/} folder.
\section{Baselines and Hyperparameters}
\textbf{Baseline A (Student A):} TF-IDF (1--2grams, 10k features) + Logistic Regression (saga solver, class\_weight=balanced).\\
\textbf{Baseline B (Student B):} Bi-LSTM with 100-dim embedding, Bi-LSTM(64), GlobalMaxPool, Dense(64). Trained with Adam and early stopping.\\
\textbf{Baseline C (Student C):} TF-IDF + LinearSVC (10k features).\\
\section{Results}
Validation metrics are saved in \texttt{results/baseline_metrics.csv}. Example values (fill after running):

\begin{table}[ht]
\centering
\caption{Validation results}
\begin{tabular}{lcc}
\toprule
Baseline & Val Acc & Val F1-macro \\ \midrule
A\_TFIDF\_LR & 0.000 & 0.000 \\
B\_BiLSTM    & 0.000 & 0.000 \\
C\_TFIDF\_SVC& 0.000 & 0.000 \\ \bottomrule
\end{tabular}
\end{table}

\section{Implementation Notes}
All code is in \texttt{code/}. Run \texttt{code/train.py} then \texttt{code/evaluate.py} to produce the plots (PDF). Use Google Colab for reproducible environment with GPU for faster Bi-LSTM training.

\section{Author Contribution}
\begin{tabular}{lll}
\toprule
Student & Task & Files \\ \midrule
Student A & Baseline A implementation, EDA plot & model\_baseline\_A.py, data\_loader.py \\
Student B & Bi-LSTM training, loss curve & model\_baseline\_B.py, train.py \\
Student C & Baseline C, metrics comparison & model\_baseline\_C.py, evaluate.py \\ \bottomrule
\end{tabular}

\section{Conclusion}
The implemented baselines provide a solid starting point. Future work includes transformer fine-tuning and augmentation.
\end{document}
